```{r setup-report, include=FALSE, echo=FALSE}
source("https://ipese-internal.epfl.ch/osmose/report-setup.R")
```
```{r, Base variables, echo=F, eval=T}
df_colors       <- read.csv2("layer_colors.csv",colClasses = "character", sep = ",")
scenario      <- 1 # TODO: insert in loop for child document
data            <- fromJSON("<<YOUR-JSON-FILE>>.json", flatten=FALSE)
n_timesteps    <- length(data$evaluated[[scenario]]$time)
n_scenarios     <- length(data$results$KPIs[[1]]) # TODO: check with length(data$evaluated)
```

# Osmose Execution Report {-}

This is a report of the Osmose simulation

Objective Optimizing : _`r data$results$solvers$hc$"_objname"`_ <br>
opex: `r data$results$KPIs$opex`  <br>
capex: `r data$results$KPIs$capex`  <br>
impact: `r data$results$KPIs$impact` <br>

Total cost: **`r data$results$KPIs$totalcost`** <br>
Operating cost with impact: **`r data$results$KPIs$opcostwithimpact`** <br>
Total cost with impact: **`r data$results$KPIs$totalcostwithimpact`** <br>
Total investment cost : **`r data$result$KPIs$totalinvestmentcost`** <br>

Number of time steps: _`r n_timesteps`_


```{r Key Performance Indicator, echo=FALSE, eval = TRUE}
kpi <- data$results$KPIs
kpi_scenarios <- data.frame(data$results$KPIs[c("opex", "capex")]) %>%
    slice(1:n_scenarios)

bar_plot(kpi_scenarios, "relative","scenarios",'Annualised cost [CHF/year]') %>%
  plotly::layout(title = "Total operating and capital costs")
```
## Costs breakdown {-}

### Investment costs {-}

```{r investment cost}
invCosts <- data$results$Units_Cost$DefaultInvCost
invCosts[is.na(invCosts)] <- 0
colnames(invCosts)  <- sub("(.*?_.*?_.*?_)","",colnames(invCosts))
nr <- nrow(invCosts)
invCostsScenario <- invCosts %>% mutate(scenarios = sprintf("Scenario %d", 1:nr))

invCosts_figure <- plot_ly(invCostsScenario, type= 'bar')
for (i in colnames(invCostsScenario)){
  if (i != "scenarios") {
    invCosts_figure <- invCosts_figure %>%
          add_trace(x=invCostsScenario[['scenarios']], y=invCostsScenario[[i]], name = i)
  }
}
invCosts_figure <- invCosts_figure %>% layout(yaxis = list(title = 'Total investment cost [CHF/Y]'), barmode = 'stack')
invCosts_figure
```


```{r investment cost table}
invCostsDF <- data.frame(t(invCosts))
colnames(invCostsDF) <- paste('Scenario', 1:length(invCostsDF))
kable(
  invCostsDF,
  format = get_output_format_for_kable()
)
```

### Operating Costs {-}

```{r operating cost}
opCosts <- data$results$Units_Cost$DefaultOpCost
opCosts[is.na(opCosts)] <- 0
colnames(opCosts)  <- sub("(.*?_.*?_.*?_)","",colnames(opCosts))
nr <- nrow(opCosts)
opCostsScenario <- opCosts %>% mutate(scenarios = sprintf("Scenario %d", 1:nr))

opCosts_figure <- plot_ly(opCostsScenario, type= 'bar')
for (i in colnames(opCostsScenario)){
  if (i != "scenarios") {
    opCosts_figure <- opCosts_figure %>%
          add_trace(x=opCostsScenario[['scenarios']], y=opCostsScenario[[i]], name = i)
  }
}
opCosts_figure <- opCosts_figure %>% layout(yaxis = list(title = 'Total operating cost [CHF/Y]'), barmode = 'stack')
opCosts_figure
```

```{r operating cost table}
opCostsDF <- data.frame(t(opCosts))
colnames(opCostsDF) <- paste('Scenario', 1:length(opCostsDF))
knitr::kable(
  opCostsDF,
  format = get_output_format_for_kable()
)
```

### Total costs {-}

```{r total cost}
totCosts <- opCosts + invCosts

nr <- nrow(totCosts)
totCostsScenario <- totCosts %>% mutate(scenarios = sprintf("Scenario %d", 1:nr))

totCosts_figure <- plot_ly(totCostsScenario, type= 'bar')
for (i in colnames(totCostsScenario)){
  if (i != "scenarios") {
    totCosts_figure <- totCosts_figure %>%
          add_trace(x=totCostsScenario[['scenarios']], y=totCostsScenario[[i]], name = i)
  }
}
totCosts_figure <- totCosts_figure %>% layout(yaxis = list(title = 'Total operating cost [CHF/Y]'), barmode = 'stack')
totCosts_figure
```

```{r total cost table}
totCostsDF <- data.frame(t(totCosts))
colnames(totCostsDF) <- paste('Scenario', 1:length(totCostsDF))
knitr::kable(
  totCostsDF,
  format = get_output_format_for_kable()
)
```

## Units resume {-}

### Units used at time t {-}

```{r unit use t, echo=FALSE, eval = TRUE}
unit_Use_t <- data.frame(data$results$Units_Use_t) %>%
        slice(scenario)
unit_use_t_list <- enframe(as.list(unit_Use_t))
list <- rbind(unit_use_t_list$value)
colnames(list) <- unit_use_t_list$name
unit_use_t_list <- as.data.frame(list)
unit_use_t <- data.frame(t(data.frame(flatten(list))))
colnames(unit_use_t) <- sprintf(paste("timestep","%s"), 1:length(unit_use_t))
rownames(unit_use_t) <- names(unit_use_t_list)
rownames(unit_use_t)  <- sub("(.*?_.*?_.*?_)","",rownames(unit_use_t))

knitr::kable(
  unit_use_t,
  format = get_output_format_for_kable()
)

if(n_timesteps > 1){
  unit_use_t <- unit_use_t[ order(row.names(unit_use_t)), ]
  unit_use_t[is.na(unit_use_t)] <- 0
  unit_use_t$used <- ifelse(rowSums(unit_use_t == 1) > 0, 1, 0)
  # unit_use_t$unit <- rownames(unit_use_t)
  mat <- as.matrix(unit_use_t)
  plot_ly(x=colnames(mat), y=rownames(mat), z=mat, colors=colorRamp(c("red", "green")), type="heatmap", showscale=F) %>%
          layout(title="Use of units")
}
```

### Units size percentage {-}

```{r unit size percentage}
fmax <- data$evaluated[[scenario]]$fmaxUnits[[1]]
rownames(fmax) <- fmax$fmaxUnitName
units_mult <- data$results$Units_Mult
units_mult <- as.data.frame(t(units_mult))
units_mult$name <- rownames(units_mult)
colnames(units_mult) <- c("value", "name")
merged_df <- merge(fmax, units_mult, by=0, all=T) %>%
  mutate(percent=(value * 100)/fmaxValue)
merged_df$name  <- sub("(.*?_.*?_.*?_)","",merged_df$name)

plot <- ggplot(merged_df, aes(x = name, y = percent)) +
        geom_bar(stat="identity", fill="steelblue") +
        coord_flip() +
        ggtitle("Size percentage used for all units") +
        ylab("percentage of use [%]") +
        xlab("") +
        ylim(0,100) +
        theme_minimal()
ggplotly(plot)
```


### Units Multiplication (size) {-}

```{r unit mult table}
unit_mult <- data.frame(data$results$Units_Mult) %>%
        slice(scenario)
unit_mult_list <- enframe(as.list(unit_mult))
list <- rbind(unit_mult_list$value)
colnames(list) <- unit_mult_list$name
unit_mult_list <- as.data.frame(list)
unit_mult <- data.frame(t(data.frame(flatten(list))))
colnames(unit_mult) <- sprintf("Value")
rownames(unit_mult) <- names(unit_mult_list)
rownames(unit_mult)  <- sub("(.*?_.*?_.*?_)","",rownames(unit_mult))

knitr::kable(
  unit_mult,
  format = get_output_format_for_kable()
)
```

### Units Multiplication (size) at time t {-}

```{r unit mult t}
unit_mult_t <- data.frame(data$results$Units_Mult_t) %>%
        slice(scenario)
unit_mult_t_list <- enframe(as.list(unit_mult_t))
list <- rbind(unit_mult_t_list$value)
colnames(list) <- unit_mult_t_list$name
unit_mult_t_list <- as.data.frame(list)
unit_mult_t <- data.frame(t(data.frame(flatten(list))))
colnames(unit_mult_t) <- sprintf(paste("timestep","%s"), 1:length(unit_mult_t))
rownames(unit_mult_t) <- names(unit_mult_t_list)
rownames(unit_mult_t)  <- sub("(.*?_.*?_.*?_)","",rownames(unit_mult_t))

knitr::kable(
  unit_mult_t,
  format = get_output_format_for_kable()
)

if(n_timesteps > 1){
  unit_mult_t <- unit_mult_t[ order(row.names(unit_mult_t)), ]
  unit_mult_t[is.na(unit_mult_t)] <- 0
  mat <- as.matrix(unit_mult_t)
  plot_ly(x=colnames(mat), y=rownames(mat), z=mat, colors="Greens", type="heatmap") %>%
          layout(title="Unit Mult T")
}
```

## Thermal streams {-}

### Temperature streams {-}


```{r heat streams}
heat_streams <- function(time=1) {
  heat_df <- data$evaluated[[1]]$streams[[time]]
  heat_df$Tin_corr <- heat_df$Tin_corr - 273.15
  heat_df$Tout_corr <- heat_df$Tout_corr - 273.15
  heat_df$name <- sub("(.*?_.*?_.*?_)","",heat_df$name)
  heat_df <- heat_df %>%
          mutate(tin = ifelse (hout > hin, Tin_corr - dt, Tin_corr + dt)) %>%
          mutate(colour = ifelse (hout > hin, "red", "blue")) %>%
          mutate(base = ifelse (hout > hin, Tin_corr, Tout_corr)) %>%
          mutate(diff = ifelse (hout > hin, Tout_corr, Tin_corr)) %>%
          mutate(tout = ifelse (hout > hin, Tout_corr - dt, Tout_corr + dt))

  plot <- ggplot(data = heat_df)+
          geom_segment(aes(x = name, xend = name, y = base, yend = diff), col = heat_df$colour, size = 15, alpha = 0.5) +
          geom_point(aes(x=name, y=tin), shape=18, size=0.5, col = heat_df$colour) +
          geom_point(aes(x=name, y=tout), shape=18, size=0.5, col = heat_df$colour) +
          coord_flip() +
          ggtitle(sprintf(paste("Heat exchange for Time","%s"), time)) +
          ylab("Temperature [°C]") +
          xlab("") +
          theme_minimal()
  ggplotly(plot)
}

heat_streams(1)
```

<br>

```{r, Heat cascade, echo=F, eval = TRUE}
unit_h_mult <- data.frame(data$results$streamQ) %>%
        slice(scenario)
unit_h_mult_list <- enframe(as.list(unit_h_mult))
list <- rbind(unit_h_mult_list$value)
colnames(list) <- unit_h_mult_list$name
unit_h_mult_list <- as.data.frame(list)
unit_h_mult <- data.frame(t(data.frame(flatten(list))))
colnames(unit_h_mult) <- sprintf(paste("timestep","%s"), 1:length(unit_h_mult))
rownames(unit_h_mult) <- names(unit_h_mult_list)

link_evaluated <- data$evaluated[[scenario]]   # take the scenario

evaluated_streams <- data$evaluated[[scenario]]$streams[[1]]
for(name in rownames(unit_h_mult)) {
  hout <- evaluated_streams[evaluated_streams$name==name,]$hout
  hin <- evaluated_streams[evaluated_streams$name==name,]$hin
  if (hout < hin){
    unit_h_mult[name,] <- unit_h_mult[name,] * (-1)
  }
}
rownames(unit_h_mult)  <- sub("(.*?_.*?_.*?_)","",rownames(unit_h_mult))

unit_h_mult <- unit_h_mult[ order(row.names(unit_h_mult)), ]
unit_h_mult[is.na(unit_h_mult)] <- 0
mat <- as.matrix(unit_h_mult)
plot_ly(x=colnames(mat), y=rownames(mat), z=mat,
        colors=colorRampPalette(c("blue", "#FFFFFF","red"))( 17 ),
        type="heatmap",
        colorbar=list(title="HEAT [kW]")) %>%
         layout(title="Heat at Time")

```


### Grand Composite Curve {-}

```{r gcc}
display_gcc <- function(time=1){
  graphs <- data$results$graph[[1]]
  graph <- graphs[[time]]
  graph <- graph[graph$plot_type == "gcc",]$data[[1]]
  gcc <- graph$curve[[1]]

  if (!is_empty(gcc)){
    plot_ly() %>%
            
      add_trace(x=gcc$Q, y=gcc$T-273.15, mode = 'lines', line=list(color='blue'), marker=list(color='blue'), name='GCC') %>%
      layout(xaxis= list(title = "Heat load [kW]"),
             yaxis= list(title = "Corrected Temperatures [C]"),
             yaxis2 = list(overlaying = "y", side = "right", title = 'Carnot factor 1-To/T [-]'),
             margin= list(l=50, r=50, b=40, t=40),
             title = "Grand Composite Curve with T0 = 298.15 K"
            )
  } else {
    print(paste("There is no GCC for timestep", time))
  }
}

display_gcc(1)
```


### Composite Curve {-}

```{r cc}
display_cc <- function(time=1){
  graphs <- data$results$graph[[1]]
  graph <- graphs[[time]]
  graph <- graph[graph$plot_type == "cc",]$data[[1]]
  hcc <- graph[graph$title == "Hot streams",]$curve[[1]]
  ccc <- graph[graph$title == "Cold streams",]$curve[[1]]

  if (!is_empty(hcc) && !is_empty(ccc)){
    plot_ly() %>%
            add_trace(x=hcc$Q, y=hcc$T-273.15, mode = 'lines', line=list(color='red'), marker=list(color='red'), name='Hot Stream') %>%
            add_trace(x=ccc$Q, y=ccc$T-273.15, mode = 'lines', line=list(color='blue'), marker=list(color='blue'), name='Cold Streams') %>%
            layout(xaxis= list(title = "Heat load [kW]"),
                   yaxis= list(title = "Corrected Temperatures [°C]"),
                   yaxis2 = list(overlaying = "y", side = "right", title = 'Carnot factor 1-To/T [-]'),
                   margin= list(l=50, r=0, b=40, t=40),
                   title = "Composite Curve with T0 = 298.15 K"
            )
    

  } else {
    print(paste("There is no CC for timestep", time))
  }
}

display_cc(1)
```

### Integrated Composite Curve{-}

```{r icc}
display_icc <- function(time=1){
  graphs <- data$results$graph[[1]]
  graph <- graphs[[time]]
  graph <- graph[graph$plot_type == "icc.utilities",]$data[[1]]
  base <- graph[graph$title == "base",]$curve[[1]]
  utilities <- graph[graph$title == "utilities",]$curve[[1]]

  if (!is_empty(base) && !is_empty(utilities)){
    plot_ly() %>%
            add_trace(x=base$Q, y=base$T-273.15, mode = 'lines', line=list(color='red'), marker=list(color='red'), name='base') %>%
            add_trace(x=utilities$Q, y=utilities$T-273.15, mode = 'lines', line=list(color='blue'), marker=list(color='blue'), name='utilities') %>%
            layout(xaxis= list(title = "Heat load [kW]"),
                   yaxis= list(title = "Corrected Temperatures [C]"),
                   margin= list(l=50, r=20, b=40, t=40),
                   yaxis2 = list(overlaying = "y", side = "right", title = 'Carnot factor 1-To/T [-]'),
                   title = "Integrated Composite Curve with T0 = 298.15 K"
            )

  } else {
    print(paste("There is no ICC for timestep", time))
  }
}

display_icc(1)
```

### Carnot{-}

```{r carnot}
display_carnot <- function(time=1){
  graphs <- data$results$graph[[1]]
  graph <- graphs[[time]]
  graph <- graph[graph$plot_type == "carnot.utilities",]$data[[1]]
  base <- graph[graph$title == "base",]$curve[[1]]
  utilities <- graph[graph$title == "utilities",]$curve[[1]]

  if (!is_empty(base) && !is_empty(utilities)){
    plot_ly() %>%
            add_trace(x=base$Q, y=base$T, mode = 'lines', line=list(color='red'), marker=list(color='red'), name='base') %>%
            add_trace(x=utilities$Q, y=utilities$T, mode = 'lines', line=list(color='blue'), marker=list(color='blue'), name='utilities') %>%
            layout(xaxis= list(title = "Heat load [kW]"),
                   yaxis= list(title = "Carnot factor 1-To/T [-]"),
                   margin= list(l=50, r=20, b=40, t=40),
                   title = "Carnot with T0 = 298.15 K"
            )

  } else {
    print(paste("There is no Carnot for timestep", time))
  }
}

display_carnot(1)
```

### HEN Area {-}

```{r}
get_HEN <- function () {
  spag_area <- data$results$spaghetti[[1]]$Clu.DefaultHeatCascade.area_total
  min_number_HEX <- data$results$spaghetti[[1]]$Clu.DefaultHeatCascade.HEs
  hex_area <- spag_area / min_number_HEX
  an_factor <- 0.10
  c_hen <- (8500 + 409 * hex_area^(0.85)) * min_number_HEX * 603.1/402 * an_factor
  return(list("hex_area" = hex_area, "an_factor" = an_factor, "c_hen"= c_hen))
}

hen <- get_HEN()
```

hex area : `r hen$hex_area`
an factor : `r hen$an_factor`
c hen : `r hen$c_hen`
